%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% acknowledge.tex: Acknowledgements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

There are many people that have earned my gratitude for their contribution to my
time in graduate school. 
First, I would like to thank my adviser, Joe Kapusta, for giving me the opportunity to begin my research career, and for guiding my research during my time at Minnesota.

I would also like to thank Tom Kelley, who helped guide me through the beginnings of my research and helped me understand the basics of the AdS/CFT correspondence.

My graduate school experience was shaped by my participation in the Department of Energy Office of Science Graduate Fellowship for three years. 
The research support for travel made my graduate career a great experience, and the camaraderie with the other fellows was also fulfilling.
I would like to thank Dr. Ping Ge, Cayla Stephenson, Igrid Gregory, and everyone else who made the DOE SCGF program a fulfilling, eye-opening experience.

Finally, I would like to thank the members of my thesis defense committee: Ron Poling, Tony Gherghetta, and Tom Jones.

This research is supported by the Department of Energy Office of Science Graduate Fellowship Program (DOE SCGF), made possible in part by the American Recovery and Reinvestment Act of 2009, administered by ORISE-ORAU under contract no. DE-AC05-06OR23100, by the US Department of Energy (DOE) under Grant No. DE-FG02-87ER40328, and by a Doctoral Dissertation Fellowship from the University of Minnesota.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
